Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-13 paper.tex
Change title to include a description of the Blue Obelisk. I think this is better if people don't know what the BO is in the first place.
Add Figure 1 - The Blue Obelisk logo
Finish off OpenSMILES

\title{The Blue Obelisk five years on}

@@

@@

\section*{Figures}
  \subsection*{Figure 1 - Sample figure title}
      A short description of the figure content
      should go here.

>>>>

\title{Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on}

@@

Despite its widespread use, a formal
definition of the language did not exist beyond Daylight's SMILES
Theory Manual and tutorials. This caused some confusion in the
implementation and interpretation of corner cases, for example the
handling of cis/trans bond symbols at ring closures. In 2007, Craig
James (eMolecules) initiated work on the OpenSMILES specification, a
complete specification of the SMILES language as an Open Standard
developed through a community process. The specification is largely
complete and contains guidelines on reading SMILES, a formal
grammar, recommendations on standard forms when writing SMILES, as
well as proposed extensions.

@@

\section*{Figures}
  \subsection*{Figure 1 - Blue Obelisk logo}
